### 2018-07-03 pack/prv/opt/tokipona/aux/article/acm/samplebody-journals.tex
feita implementacao mais decente via classe da wordnet de tp

The \tttt{TPWordnet} class~\cite{tokipona},
provides such tentative TP Wordnets in their simplest form:
the TP words are keys in a dictionary that returns the
corresponding synsets.
Three of such dictionaries are implemented:
one where all synsets related to the lemma is
returned (the version most consistent
with the expositions in Section~\ref{basics}),
with 4,052 synsets;
another as such but excluding the prepositions,
with 3,961 synsets;
a last one that returns only the synsets
registered in Wordnet with the same POS tag as the lemma
is in the official dictionary,
with 2,493 synsets. 
Another immediate possibility, not implemented,
would be to relate each Toki Pona word to the synsets
simultaneously associated to all the English
words bounded by a semicolon in the dictionary.
Such collection of synsets, and its relation to the whole
Wordnet
(the total number of synsets in Wordnet is $117,659$),
might guide creation of other conlangs
(e.g. one might seek to use lemmas related to synsets that
are very far apart, or that has the most complete neighborhood
possible).
% Total number of synsets counting neighbors is Y. TTM
% Depth of TP synsets is .

>>>>

The \tttt{TPWordnet} class~\cite{tokipona},
provides such tentative TP Wordnets in their simplest form:
the TP words are keys in a dictionary that returns the
corresponding synsets.
Three of such dictionaries are implemented:
one where all synsets related to the lemma is
returned (the version most consistent
with the expositions in Section~\ref{basics}),
with 4,027 synsets;
another as such but excluding the prepositions,
with 3,929 synsets;
a last one that returns only the synsets
registered in Wordnet with the same POS tag as the lemma
is in the official dictionary,
with 2,462 synsets. 
Another immediate possibility, not implemented,
would be to relate each Toki Pona word to the synsets
simultaneously associated to all the English
words bounded by a semicolon in the dictionary.
Such collection of synsets, and its relation to the whole
Wordnet
(the total number of synsets in Wordnet is $117,659$),
might guide creation of other conlangs
(e.g. one might seek to use lemmas related to synsets that
are very far apart, or that has the most complete neighborhood
possible).
% Total number of synsets counting neighbors is Y. TTM
% Depth of TP synsets is .
